An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
some minor edits

Our primary motivation was {\em freedom}: we wanted a system where
the software and exercises could be freely redistributed, and
were not under the control of any central authority.  This motivation
is not entirely philosophical: we felt that locking down either
the software or the exercises would result in a barrier to adoption,
limiting the potential impact of the system.
As we will discuss in Section~\ref{sec:questions}, we think that there
are some interesting research questions that can be addressed
best through the existence of a ``free like air'' programming
exercise system: for example, we are very interested in finding out
whether exercises can be reused effectively in different courses
at different institutions.

@@

\section{CloudCoder}
We have designed CloudCoder to be an open platform for managing short
programming exercises.  The CloudCoder platform has four design
goals:  To be an open-platform for faculty to assign short programming
exercises, to build a collection of redistributable programming
exercises, to collect data about student behaviors as they solve
exercises, and to explore ways of curating the collected data.

@@

CloudCoder is an open platform for managing short programming
exercises.  Each exercise can be solved with one method or one short
program, and could take only a few minutes to solve, or could require
or an hour or two.  The system is not designed to support longer
programming assignments, such as those found at the {\em Nifty
Assignments} session at SIGCSE.

Figure~\ref{screenshot} shows a screenshot of a CloudCoder exercise.
The editor is derived from the Ace editor \cite{ace}, and supports
syntax high-lighting for most programming languages, and
auto-indentation.  
A submit button runs the code against a series of
test cases, and feedback is provided directly in the browser.
CloudCoder captures anything the code prints to standard out or
standard err to help students with debugging.

>>>>

Our primary motivation in developing CloudCoder
was {\em freedom}: we wanted a system where
the software and exercises could be freely redistributed, and
were not under the control of any central authority.  This motivation
is not entirely philosophical: we felt that locking down either
the software or the exercises would result in a barrier to adoption,
limiting the potential impact of the system.
As we will discuss in Section~\ref{sec:questions}, we think that there
are some interesting research questions that can be addressed
best through the existence of a ``free like air'' programming
exercise system: for example, we are very interested in finding out
whether exercises can be reused effectively in different courses
at different institutions.

@@

\section{CloudCoder}
%We have designed CloudCoder to be an open platform for managing short
%programming exercises.  The CloudCoder platform has four design
%goals:  To be an open-platform for faculty to assign short programming
%exercises, to build a collection of redistributable programming
%exercises, to collect data about student behaviors as they solve
%exercises, and to explore ways of curating the collected data.

In this section, we describe CloudCoder and discuss some initial experiences
using it in introductory courses at several colleges and universities.

@@

CloudCoder is an open platform for managing short programming
exercises.
Each exercise can be solved with one method or one short
program, and could take only a few minutes to solve, or could require
or an hour or two.  The system is not designed to support longer
programming assignments, such as those found at the {\em Nifty
Assignments} session at SIGCSE \cite{Parlante:2013:NA:2445196.2445356}.

Figure~\ref{screenshot} shows a screenshot of a CloudCoder exercise.
The editor is derived from the Ace editor \cite{ace}, and supports
syntax high-lighting for most programming languages, and
auto-indentation.  
A submit button runs the code against a series of
test cases, and feedback is provided directly in the browser.
CloudCoder captures the code's standard output and
standard error streams to help students with debugging.
